---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OaxacaBlinder

<!-- badges: start -->

[![experimental](http://badges.github.io/stability-badges/dist/experimental.svg)](http://github.com/badges/stability-badges)

<!-- badges: end -->

This is an R implementation of `OaxacaBlinder` decomposition that comes with

- correction for dummy encoding baseline with multiple factors
- more convenient output formatting

Please also check the stable `oaxaca` package on CRAN.

## Installation

You can install the development version of `OaxacaBlinder` like so:

``` r
# install.packages("remotes")
remotes::install_github("SinanPolatoglu/OaxacaBlinder")
```

## Example

Using the chicago dataset from the `oaxaca` package

```{r}
library(OaxacaBlinder)
dplyr::glimpse(chicago_long)
```


### Twofold decomposition

- The formula interface is similar to the `oaxaca` package: it should be specified as `dependent_var ~ x_var1 + x_var1 + ... + x_varK | group_var`.
- OaxacaBlinder is capable of correcting for the ommitted baseline bias for multipe sets of factor variables with the `baseline_invariant=TRUE`
- The `pooled` argument sets what reference $\beta_R$:
  - `neumark`: The parameters of a model **excluding** the group variable
  - `jann`: The parameters of a model **including** the group variable

```{r}
twofold = OaxacaBlinderDecomp(
  formula = real_wage ~ age + education | female,
  data = chicago_long,
  type = "twofold",
  baseline_invariant = TRUE,
  n_bootstraps = 100
)
summary(twofold)
```

In addition, coefficients can be extracted vor the variable-level estimates

```{r}
coef(twofold)
```

Or with bootstrapped confidence intervals for variable level results

```{r}
coef(twofold, ci=TRUE)
```

### Threefold decomposition

```{r}
threefold = OaxacaBlinderDecomp(
  real_wage ~ age + education | female, chicago_long,
  type = "twofold",
  pooled = "jann",
  baseline_invariant = TRUE
)
summary(threefold)
coef(threefold)
```
