---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OaxacaBlinder

<!-- badges: start -->
<!-- badges: end -->

This is an R implementation of the bare-bones version of `OaxacaBlinder`.
It aims to provide a more intuitive interface in R

## Installation

You can install the development version of OaxacaBlinder like so:

``` r
remotes::install_github("SinanPolatoglu/OaxacaBlinder")
```

## Example

```{r}
library(OaxacaBlinder)
dplyr::glimpse(glassdoor_gpg)
```

The formula interface is similar to the `oaxaca` package.
It should be specified as `dependent_var ~ x_var1 + x_var1 + ... + x_varK | group_var`. Note that the interface supports supplying factor variables to the formula and `x_var*` can represent a nominal variable such as further in the document.

### Twofold decomposition

```{r}
twofold = OaxacaBlinderDecomp(BasePay ~ Dept + Age | Gender_i, glassdoor_gpg, type = "twofold")
summary(twofold)
```

In addition, coefficients can be extracted vor the variable-level estimates

```{r}
coef(twofold)
```

### Threefold decomposition

```{r}
threefold = (OaxacaBlinderDecomp(BasePay ~ Dept + Age | Gender_i, glassdoor_gpg, type = "threefold"))
summary(threefold)
coef(threefold)
```
